Jeff Goldsmith

### 2017-09-05 papers.Rmd
updating papers page with a couple of recent things

## 2017

A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
Habitual selection of reaction times.
<i> eLife, </i> 
accepted.

@@

P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
Methods for Scalar-on-Function Regression (2017+).
<i> International Statistical Review, </i>
<b>85</b> 228-249.

>>>>

## 2017
D. Backenroth<sup>&#8225;</sup>, **J. Goldsmith**, M. D. Harran, J. C. Cortes, J. W. Krakauer, and T. Kitago (2017+).
Modeling motor learning using heteroskedastic functional principal components analysis.
<i> Journal of the American Statistical Association, </i> 
accepted.
[[PDF](Downloads/HetFCPA.pdf)]

M. S. Maurer, E. Horn, A. Reyentovich, V. V. Dickson, S. Pinney, D. Goldwater, N. E. Goldstein, O. Jimenez, S. Teruya, **J. Goldsmith**, S. Helmke, M. Yuzefpolskaya, and G. R Reeves (2017+).
Can a Left Ventricular Assist Devices in Advanced Systolic Heart Failure Improve or Reverse the Frailty Phenotype?
<i> Journal of the American Geriatrics Society, </i> accepted.

@@

A. L. Wong, **J. Goldsmith**, A. D. Forrence, A. M. Haith, and J. W. Krakauer (2017+).
Habitual selection of reaction times.
<i> eLife, </i> 
<b>6</b> e28075.
[[Link](https://elifesciences.org/articles/28075)]

P. T. Reiss, **J. Goldsmith**, H. L. Shang, and R. T. Ogden.
Methods for Scalar-on-Function Regression (2017).
<i> International Statistical Review, </i>
<b>85</b> 228-249.
